\label{sec:bibliography}
\begin{thebibliography}{9}
\bibitem{mcnpfundamentals}
Forrest B. Brown 
\textit{Fundamentals of Monte Carlo Particle Transport}.
Los Alamos National Laboratory, 1996.
 
\bibitem{beginningmcnp}
Nicholas Metropolis
\textit{The Beginning of the Monte Carlo Method}.
Los Alamos Science Special Edition, 1987.
 
\bibitem{metropolis}
Herbert L. Anderson
\textit{Metropolis, Monte Carlo and the MANIAC}.
Los Alamos National Laboratory, 1986.

\bibitem{manual}
Herbert L. Anderson
\textit{MCNP - A general Monte Carlo N-Particle Transport Code, Version 4C}.
Los Alamos National Laboratory, 2000.

\bibitem{source}
Esam Hussein
\textit{Monte Carlo Particle Transport with the MCNP Code}.
University of New Brunswick, 2006

\bibitem{materials}
Roger Williams III, Christopher Gesh, Rajesh Pagh
\textit{Compendium of Material Composition Data for Radiation Transport Modeling}.
Pacific Northwest National Laboratory, 2006

\bibitem{primer}
Jack Shultis, Robert Faw
\textit{An MCNP Primer}.
Kansas State University, 2011

\bibitem{simulation}
Sean Conroy
\textit{Simulation using MCNP}.
Uppsala university, Chapters 5, 6, 2017

\bibitem{scattering}
Andrew Jackson
\textit{Introduction to Small-Angle Neutron Scattering and Neutron Reflectometry}.
NIST Center for Neutron Research, 2008

\bibitem{tablevalues}
Alan Munter
\textit{Neutron Scattering Lengths and cross sections}.
Neutron News, Vol. 3, No. 3,pp. 29-37, 1992

\bibitem{conversion}
Alan Munter
\textit{Progress, Challenges, and Opportunities for Converting U.S. and Russian Research Reactors: A Workshop Report}.
National Research Council of the National Academies, Chapter 3, 2012

\bibitem{fuels}
\textit{TRIGA Fuels}.
General Atomics and Affiliated Companies, 2017

\bibitem{patent}
Bagge Erich Rudolf
\textit{Nuclear reactor with solid substance moderator of variable slowing-down power}.
United States Patent US-336163-6, 2017

\bibitem{newfuel}
Takuya Yamamoto, Hadi Suwarno, Hideo Kayano, Michio Yamawaki
\textit{Development of New Reactor Fuel Materials}.
Journal of Nuclear Science and Technology, 1995

\bibitem{umassconversion}
Dr. John R. White, Justin Byard, and Areeya Jirapongmed 
\textit{Computational Support for the HEU to LEU Conversion of the UMLRR}.
University of Massachusetts Lowell, 1995

\bibitem{umassconversion}
Anwar A. Rahman, Mohd Arif Hamzah, Julia A. Karim, Rosli Darmawan
\textit{Current Progress and preliminary shielding design analysis for Gamma cell using MCNP}.
Malaysian Nuclear Energy, 2013
\end{thebibliography}